---
title: "sentiment_detection"
author: "Frederick"
date: "June 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	cache = TRUE
)
```


```{r}
library(scales)
library(tidyverse)
theme_set(theme_light())

og_ads <- read_csv("../data/textsim_queries/og_ad.csv")
cands <- read_csv("../data/candidate_images/cand_image_data.csv")


```


* Queried over 2 days (3/18/2019 - 3/19/2018)
* 674 distinct funding entities (top heavy, can fct_lump)
* 801 unique page_id/page_name
* 52,615 unique ads
* Impression: number of people impacted by ad?
  * most ads have number of impressions: have some outliers who are huge
* All but two are currency US


```{r}
last_day <- as.POSIXct("2019-03-19 23:59:59", format = "%Y-%m-%d %H:%M:%S", tz = "UTC")
# Democratic Congressional Campaign Committee
# National Republican Congressional Committee
big_groups <- c("Priorities USA Action", "NRCC", "DCCC", 
                "Senate Leadership Fund", "Senate Majority PAC","SMP",
                "House Majority PAC", "Congressional Leadership Fund", 
                "Forward Majority Action", "Majority Forward",
                "Americans for Prosperity", "AFP")


big_groups_pat <- paste0("(?i)(", paste0(c(big_groups), collapse = ")|("), ")(?-i)")
big_groups_pat
not_authorized_pat <- "(and|\\.|,) (?i)(not authorized by|(not affiliated with))(?-i) (.)*$"

distinct_ads <- og_ads %>% 
  distinct(ad_id, page_id, .keep_all = TRUE) %>% 
  replace_na(list(ad_delivery_stop_time = last_day)) %>% 
  mutate(hours_up = as.numeric(ad_delivery_stop_time - ad_delivery_start_time),
         impressions_mean = (impressions.lower_bound + impressions.upper_bound) / 2) %>% 
  select(ad_id, page_id, page_name, funding_entity, ad_creative_body,hours_up, impressions_mean)

ad_funds_clean <- distinct_ads %>% 
  mutate(not_authorized = str_extract(funding_entity, not_authorized_pat),
         not_authorized = str_detect(not_authorized, "[a-z]"),
         clean_entities1 = str_extract(funding_entity, big_groups_pat),
         clean_entities1 = coalesce(clean_entities1, "Other"),
         clean_entities1 = case_when(
           clean_entities1 == "HOUSE MAJORITY PAC" ~ "House Majority PAC",
           clean_entities1 == "Americans For Prosperity"  ~ "Americans for Prosperity",
           clean_entities1 == "AFP"  ~ "Americans for Prosperity",
           clean_entities1 == "SENATE LEADERSHIP FUND" ~ "Senate Leadership Fund",
           clean_entities1 == "SMP" ~ "Senate Majority PAC",
           TRUE ~ clean_entities1
         )) %>% 
  select(-funding_entity) %>% 
  rename(funding_entity = clean_entities1)
  



ad_funds_clean %>% 
  ggplot(aes(impressions_mean)) +
  geom_histogram(bins = 40) +
  scale_x_log10(labels = comma_format()) +
  labs(title = "How many people do the ads reach (impressions)?",
       x = "Mean No. of impressions",
       y = "")

ad_funds_clean %>% 
  ggplot(aes(hours_up)) +
  geom_histogram(bins = 40) +
  scale_x_log10(labels = comma_format())  + 
  labs(title = "How many hours are ads left up?") 

ad_funds_clean %>% 
  select(hours_up, impressions_mean, funding_entity) %>% 
  group_by(funding_entity) %>% 
  mutate(n_ads = n()) %>% 
  ungroup() %>% 
  mutate(ind = row_number(),
         funding_entity = fct_reorder(funding_entity, n_ads)) %>% 
  gather("var", "value", -ind, -funding_entity) %>% 
  mutate(var = fct_relevel(var, "n_ads", "hours_up", "impressions_mean")) %>% 
  ggplot(aes(funding_entity, value)) +
  geom_boxplot() +
  scale_y_log10(labels = comma_format())  + 
  coord_flip() + 
  facet_wrap(~ var, scales = "free_x") +
  labs(title = "Distribution of Ads by Group",
       subtitle = "Groups w/ less than 120 ads lumped into others",
       x = "Major Funding Entities",
       y = "")


```

```{r}
by_funds <- ad_funds_clean %>% 
  group_by(funding_entity) %>% 
  summarise(n_ads = n(), 
            hours_up = mean(hours_up, na.rm = TRUE),
            impressions_mean = mean(impressions_mean, na.rm = TRUE)) %>% 
  mutate(funding_entity = fct_reorder(funding_entity, n_ads))

by_funds %>% 
  gather("var", "value", -funding_entity) %>% 
  mutate(var = fct_relevel(var, "n_ads", "hours_up", "impressions_mean")) %>% 
  ggplot(aes(funding_entity, value)) +
  geom_col() + 
  coord_flip() + 
  facet_wrap(~ var, scales = "free_x") + 
  labs(title = "Ads by Group",
       subtitle = "Groups w/ less than 120 ads lumped into others",
       x = "Major Funding Entities",
       y = "")

```




# Text Analysis

What words are in ads that are up the longest? Impact the most number of people?
```{r}
library(widyr)
library(igraph)
library(ggraph)
library(tidytext)

ad_words <- ad_funds_clean %>% 
  mutate(idx = row_number()) %>% 
  unnest_tokens(word, ad_creative_body) %>% 
  anti_join(stop_words, by = "word") %>% 
  filter(str_detect(word, "[a-z]")) %>% 
  select(idx, word, funding_entity, page_name, hours_up, impressions_mean) %>% 
  distinct(idx, word, .keep_all = TRUE) 

ad_words %>% 
  group_by(funding_entity) %>% 
  count(word, sort = TRUE) %>% 
  top_n(10, n) %>% 
  ggplot(aes(word,n)) +
  geom_col() + 
  coord_flip() +
  facet_wrap(~ funding_entity, scales = "free") + 
  labs(title = "Most common words in ads by funding entity",
       x = "", 
       y = "")

```


```{r}
ad_words_filtered <- ad_words %>% 
  add_count(word) %>% 
  filter(n > 800)
ad_words_filtered %>% distinct(word)

top_word_cors <- ad_words_filtered %>% 
  select(idx, word) %>% 
  widyr::pairwise_cor(word, idx, sort = TRUE) %>% 
  head(200)

calculate_mode <- function(x) {
  uniqx <- unique(x)
  uniqx[which.max(tabulate(match(x, uniqx)))]
}

ad_words_meta <- ad_words %>% 
  filter(word %in% top_word_cors$item1 |
           word %in% top_word_cors$item2) %>% 
  group_by(word) %>% 
  summarize(hours_up = exp(mean(log(hours_up), na.rm = TRUE)),
            impressions_mean = exp(mean(log(impressions_mean), na.rm = TRUE)),
            funding_entity = calculate_mode(funding_entity)) 

mean(ad_words_meta$impressions_mean)

set.seed(12)
top_word_cors %>% 
  graph_from_data_frame(vertices = ad_words_meta) %>%
  ggraph() +
  geom_edge_link() +
  # geom_node_point(aes(size = hours_up * 1.1)) +
  geom_node_point(aes(size = hours_up,
                      color = impressions_mean)) +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_color_gradient2(low = "blue",
                        high = "red",
                        midpoint = 3000) + 
  theme_void() +
  labs(title = "What's hot and what's not in Political Ad Text?",
       subtitle = "Color shows the geometric mean of ad impressions",
       size = "Campaign Duration (hrs)",
       color = "No. of Impressions")



ggplot(aes(n)) +
  geom_histogram(bins = 40) + 
  scale_x_log10(labels = comma_format())
```


* CRP ads: who is pouring money into advertising (with page_id)
* 7 groups or